```{r, echo=FALSE}
figIndex <- 4
```

---
title: `r paste("Supplementary Figure ", figIndex, sep='')`
author: "Ziqiang Wei"
date: '`r Sys.Date()`'
output:
  html_document:
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results='asis')
```

## Parameter space of spike-to-calcium model
### Supplementary Figure `r figIndex`a -- parameter space of spike-to-calcium model, from simultaneous recordings in mice V1 areas.

### Supplementary Figure `r figIndex`b -- baseline firing rate _de facto_ influence activity profile of generated calcium activity
![](../Plot/ModelCellFits/S2CSuppRiseTime.svg)

## Transition of cell types in model
### Supplementary Figure `r figIndex`c -- example neurons that vary from dynamical to homogeneous cell type in model
```{r}
source('Dataset_Comparison_Funcs.R')
Datasets <- c('Modeled_Ca_Long_Decay_No_Noise', 'Modeled_Ca_Short_Decay_No_Noise')
DatasetsName <- c('Ca Long Decay', 'Ca Short Decay')
ImageDir <- 'S2CModel/SingleUnitsTscoreExampleNeuron_'
includeVerticalMD(ImageDir, Datasets=Datasets, DatasetsName = DatasetsName, fileType = 'svg')
```
### Supplementary Figure `r figIndex`d -- example neurons that vary from mixed-selective to homogeneous cell type in model
```{r}
source('Dataset_Comparison_Funcs.R')
Datasets <- c('Modeled_Ca_Long_Decay_No_Noise', 'Modeled_Ca_Short_Decay_No_Noise')
DatasetsName <- c('Ca Long Decay', 'Ca Short Decay')
ImageDir <- 'S2CModel/SingleUnitsAnovaExampleNeuron_'
includeVerticalMD(ImageDir, Datasets=Datasets, DatasetsName = DatasetsName, fileType = 'svg')
```

## Deconvolution models

### Supplementary Figure `r figIndex`f -- fraction of dynamical neuron

### Supplementary Figure `r figIndex`g -- fraction of mixed neuron

### Supplementary Figure `r figIndex`h -- ROC

### Supplementary Figure `r figIndex`i -- z-score


