```{r, echo=FALSE}
figIndex <- 5
```

---
title: `r paste("Supplementary Figure ", figIndex, sep='')`
author: "Ziqiang Wei"
date: '`r Sys.Date()`'
output:
  html_document:
    css: "pdfprint.css"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results='asis')
```

### Supplementary Figure `r figIndex`a -- Decodability of stimulus in subsets of neurons
Here we examined the decodability of stimulus in different subsets of neurons, which are composed of different
selectivity across trials (ROC of neuronal subpopulation are ranged from 0.5 to 0.8), as well as of different 
amounts of neurons, ranged from 100, 200, 500 or all neurons being recorded.

(spike, AAV 4.12, Transgenetic 4.3)


### Supplementary Figure `r figIndex`b -- Decodability of stimulus vs shuffle or simultaneous recorded data
(spike, AAV 4.12, Transgenetic 4.3)


### Supplementary Figure `r figIndex`d -- Decodability of epoch vs the number of neurons
(spike, AAV 4.12, Transgenetic 4.3)


### Supplementary Figure `r figIndex`e -- Decodability of epoch vs neuronal selectivity (ROC)
(spike, AAV 4.12, Transgenetic 4.3)

### Supplementary Figure `r figIndex`f -- Decodability of epoch vs shuffle or simultaneous recorded data
(spike, AAV 4.12, Transgenetic 4.3)

### Supplementary Figure `r figIndex`g -- Decodability of stimulus using spike to calcium model

### Supplementary Figure `r figIndex`h -- Decodability of epoch using spike to calcium model