```{r, echo=FALSE}
figIndex <- 6
```

---
title: `r paste("Supplementary Figure ", figIndex, sep='')`
author: "Ziqiang Wei"
date: '`r Sys.Date()`'
output:
  html_document:
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results='asis')
```


### Supplementary Figure `r figIndex`a -- PCA function as function against time
(spike, AAV 4.12, Transgenetic 4.3)


### Supplementary Figure `r figIndex`b -- PCA-PCA
(spike, AAV 4.12, Transgenetic 4.3)


### Supplementary Figure `r figIndex`c -- LDA-PCA
(spike, AAV 4.12, Transgenetic 4.3)

### Supplementary Figure `r figIndex`a -- PCA function -- simultaneous vs shuffle
(spike, AAV 4.12, Transgenetic 4.3)

### Supplementary Figure `r figIndex`d -- LDA-LDA -- simultaneous vs shuffle
(spike, AAV 4.12, Transgenetic 4.3)

### Supplementary Figure `r figIndex`e -- PCA-LDA -- simultaneous vs shuffle
(spike, AAV 4.12, Transgenetic 4.3)

### Supplementary Figure `r figIndex`f -- PCA-PCA -- simultaneous vs shuffle
(spike, AAV 4.12, Transgenetic 4.3)

### Supplementary Figure `r figIndex`g -- LDA-LDA traces using spike to calcium model