```{r, echo=FALSE}
figIndex <- 1
```
---
title: `r paste("Supplementary Figure ", figIndex, sep='')`
author: "Ziqiang Wei"
date: '`r Sys.Date()`'
output:
  html_document:
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results='asis')
```

## Fraction of dynamical-selective neurons is distributed similarly at different locations
<!-- Add neuronal activity as Fig. a -->
Here, we examined __Hypothesis I__ by sampling neurons in the same dataset according to their depths (__Supplementary Figure 1a__), anterior-to-posterior and medial-to-lateral locations(__Supplementary Figure 1b__), and animal tags(__Supplementary Figure 1c__), where, for each dataset, left panel shows the fraction of neuron type (non-selective neuron, _navy_; homogeneous-selective neuron, _green_; dynamical-selective neuron, _yellow_), and right panel shows the total number of neurons in each condition.

### Supplementary Figure `r figIndex`a -- Fraction of dynamical-selective neurons is distributed similarly at different depths
<!-- Add statistical test, p-value, maybe sharable r code -->
<style> table,td,tr,th {border:none!important} </style>
```{r}
ImageDir <- 'SingleUnitsTscore/SingleUnitsTscoreDepth_'
source('Dataset_Comparison_Funcs.R')
includeHtmlMD(ImageDir)
```

### Supplementary Figure 1b -- Fraction of dynamical-selective neurons is distributed similarly at different AP-ML locations
<!-- Add statistical test, p-value, maybe sharable r code; statistical table like number of neurons in each condition -->
```{r}
apmlDatasets <- 'SShuffleConfounding_Ca_Slow_Long_Delay'
apmlDatasetsName <- 'Transgenic: GP4.3 (Long delay)'
ImageDir <- 'ConfoundingFactorTscore/SingleUnitsTscoreAPML_'
source('Dataset_Comparison_Funcs.R')
includeHtmlMD(ImageDir, Datasets = apmlDatasets, DatasetsName=apmlDatasetsName)
```

### Supplementary Figure 1c -- Fraction of dynamical-selective neurons is distributed similarly across different animals
<!-- Add statistical test, p-value, maybe sharable r code; statistical table like number of neurons in each condition -->
```{r}
anmDatasets = c('ShuffleConfounding_Spikes', 'ShuffleConfounding_Ca_Slow_Short_Delay_Virus')
anmDatasetsName = c('Spike', 'AAV: GP4.12')
ImageDir = 'ConfoundingFactorTscore/SingleUnitsTscoreANM_'
source('Dataset_Comparison_Funcs.R')
includeHtmlMD(ImageDir, Datasets = anmDatasets, DatasetsName=anmDatasetsName)
```