```{r, echo=FALSE}
figIndex <- 1
```
---
title: `r paste("Supplementary Figure ", figIndex, sep='')`
author: "Ziqiang Wei"
date: '`r Sys.Date()`'
output:
  html_document:
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results='asis')
```

## Example neurons of dynamical-selective neurons
### Supplementary Figure `r figIndex`a
First row: homogeneous neuron; second row: dynamical neuron.
```{r}
ImageDir <- 'SingleUnitsTscore/SingleUnitsTscoreExampleNeuron_'
source('Dataset_Comparison_Funcs.R')
includeVerticalMD(ImageDir)
```

## Fraction of dynamical-selective neurons is distributed similarly at different locations
<!-- Add neuronal activity as Fig. a -->
Here, we examined __Hypothesis I__ by sampling neurons in the same dataset according to their depths (__Supplementary Figure 1b__), anterior-to-posterior and medial-to-lateral locations (__Supplementary Figure 1c__), and animal tags (__Supplementary Figure 1d__), where, for each dataset, left panel shows the fraction of neuron type (non-selective neuron, _navy_; homogeneous-selective neuron, _green_; dynamical-selective neuron, _yellow_), and right panel shows the total number of neurons in each condition.

### Supplementary Figure `r figIndex`b -- Fraction of dynamical-selective neurons is distributed similarly at different depths
<!-- Add statistical test, p-value, maybe sharable r code -->
<style> table,td,tr,th {border:none!important} </style>
```{r}
ImageDir <- 'SingleUnitsTscore/SingleUnitsTscoreDepth_'
source('Dataset_Comparison_Funcs.R')
includeHtmlMD(ImageDir)
```

### Supplementary Figure `r figIndex`c -- Fraction of dynamical-selective neurons is distributed similarly at different AP-ML locations
We analyzed using Transgenic: GP4.3 (Long delay) (whole population: 3071, sub-population: 1104)
<!-- Add statistical test, p-value, maybe sharable r code; statistical table like number of neurons in each condition -->
```{r}
apmlDatasets <- c('Pop_SShuffleConfounding_Ca_Slow_Long_Delay', 'Sub_SShuffleConfounding_Ca_Slow_Long_Delay')
apmlDatasetsName <- c('Whole population', 'Sub-population')
ImageDir <- 'ConfoundingFactorTscore/SingleUnitsTscoreAPML_'
source('Dataset_Comparison_Funcs.R')
includeHtmlMD(ImageDir, Datasets = apmlDatasets, DatasetsName=apmlDatasetsName)
```

### Supplementary Figure `r figIndex`d -- Fraction of dynamical-selective neurons is distributed similarly across different animals
<!-- Add statistical test, p-value, maybe sharable r code; statistical table like number of neurons in each condition -->
```{r}
anmDatasets = c('ShuffleConfounding_Spikes', 'ShuffleConfounding_Ca_Slow_Short_Delay_Virus')
anmDatasetsName = c('Spike', 'AAV: GP4.12')
ImageDir = 'ConfoundingFactorTscore/SingleUnitsTscoreANM_'
source('Dataset_Comparison_Funcs.R')
includeHtmlMD(ImageDir, Datasets = anmDatasets, DatasetsName=anmDatasetsName)
```