```{r, echo=FALSE}
figIndex <- 4
```

---
title: `r paste("Supplementary Figure ", figIndex, sep='')`
author: "Ziqiang Wei"
date: '`r Sys.Date()`'
output:
  html_document:
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results='asis')
```

#### Supplementary Figure 4a -- calcium to spike model (linear model)

#### Supplementary Figure 4b -- calcium to spike model (non-linear model)

#### Supplementary Figure 5a -- calcium to spike model (linear model)

#### Supplementary Figure 5b -- calcium to spike model (non-linear model)

#### Supplementary Figure 6a -- calcium to spike model (linear model)

#### Supplementary Figure 6b -- calcium to spike model (non-linear model)

#### Supplementary Figure 7a -- calcium to spike model (linear model)

#### Supplementary Figure 7b -- calcium to spike model (non-linear model)

#### Supplementary Figure 8a -- calcium to spike model (linear model)

#### Supplementary Figure 8b -- calcium to spike model (non-linear model)

#### Supplementary Figure 5a-1 -- calcium to spike model (linear model)

#### Supplementary Figure 5a-2 -- calcium to spike model (non-linear model)

#### Supplementary Figure 5b-1 -- calcium to spike model (linear model)

#### Supplementary Figure 5b-2 -- calcium to spike model (non-linear model)

#### Supplementary Figure 6a --Trade-off holds true at different depths

#### Supplementary Figure 6b -- Trade-off holds true at different AP-ML locations

#### Supplementary Figure 6c -- Trade-off holds true across different animals

#### Supplementary Figure 7a -- calcium to spike model (linear model)

#### Supplementary Figure 7b -- calcium to spike model (non-linear model)

