```{r, echo=FALSE}
figIndex <- 6
```

---
title: `r paste("Supplementary Figure ", figIndex, sep='')`
author: "Ziqiang Wei"
date: '`r Sys.Date()`'
output:
  html_document:
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results='asis')
```


### Supplementary Figure `r figIndex`a -- PCA function as function against time
Analysis based on 500 random units will be given upon request.
```{r}
source('Dataset_Comparison_Funcs.R')
ImageDir <- 'CollectedUnitsPCALDACorr/SimilarityPCA_100_'
includePieMD(ImageDir, fileType = 'svg')
```

### Supplementary Figure `r figIndex`b -- LDA-PCA
Analysis based on 500 random units will be given upon request.

```{r}
source('Dataset_Comparison_Funcs.R')
ImageDir <- 'CollectedUnitsPCALDACorr/SimilarityLDAPCA_100_'
includeColorbarMD(ImageDir, fileType = 'svg')
```

### Supplementary Figure `r figIndex`c -- LDA-LDA -- simultaneous vs shuffle
```{r}
source('Dataset_Comparison_Funcs.R')
Datasets <- c('Simultaneous_Spikes', 'Simultaneous_Ca_Slow_Short_Delay_Virus', 'Simultaneous_Ca_Slow_Short_Delay')
ImageDir <- 'SimultaneousUnitsDecodability/SimilarityLDALDA_'
includeVerticalColorbarMD(ImageDir, Datasets=Datasets, fileType = 'svg')
```

### Supplementary Figure `r figIndex`d -- PCA function -- simultaneous vs shuffle
```{r}
source('Dataset_Comparison_Funcs.R')
Datasets <- c('Simultaneous_Spikes', 'Simultaneous_Ca_Slow_Short_Delay_Virus', 'Simultaneous_Ca_Slow_Short_Delay')
ImageDir <- 'SimultaneousUnitsDecodability/SimilarityPCA_'
includeVerticalPieMD(ImageDir, Datasets=Datasets, fileType = 'svg')
```

### Supplementary Figure `r figIndex`e -- LDA-PCA -- simultaneous vs shuffle
```{r}
source('Dataset_Comparison_Funcs.R')
Datasets <- c('Simultaneous_Spikes', 'Simultaneous_Ca_Slow_Short_Delay_Virus', 'Simultaneous_Ca_Slow_Short_Delay')
ImageDir <- 'SimultaneousUnitsDecodability/SimilarityLDAPCA_'
includeVerticalColorbarMD(ImageDir, Datasets=Datasets, fileType = 'svg')
```

### Supplementary Figure `r figIndex`f -- LDA-LDA traces using spike to calcium mode