```{r, echo=FALSE}
figIndex <- 5
```

---
title: `r paste("Supplementary Figure ", figIndex, sep='')`
author: "Ziqiang Wei"
date: '`r Sys.Date()`'
output:
  html_document:
    css: "pdfprint.css"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results='asis')
```

### Supplementary Figure `r figIndex`a -- Decodability of stimulus in subsets of neurons
Here we examined the decodability of stimulus in different subsets of neurons, which are composed of different
selectivity across trials (ROC of neuronal subpopulation are ranged from 0.5 to 0.8), as well as of different 
amounts of neurons, ranged from 100, 200, 500 or all neurons being recorded.
```{r}
source('Dataset_Comparison_Funcs.R')
ImageDir <- 'CollectedUnitsDecodability/CollectedUnitsDecodabilityROC_'
includeVerticalPieMD(ImageDir, fileType = 'svg')
```

### Supplementary Figure `r figIndex`b -- Decodability of epoch in subsets of neurons
Here we examined the decodability of epoch in different subsets of neurons, which are composed of different
selectivity across trials (ROC of neuronal subpopulation are ranged from 0.5 to 0.8), as well as of different 
amounts of neurons, ranged from 100, 200, 500 or all neurons being recorded.
```{r}
source('Dataset_Comparison_Funcs.R')
ImageDir <- 'CollectedUnitsDecodabilityEpoch/CollectedUnitsDecodabilityEpoch'
includePieMD(ImageDir, Datasets = '', DatasetsName= '', fileType = 'svg')
```

### Supplementary Figure `r figIndex`c -- Decodability of stimulus using shuffled and simultaneous recorded data
Here we examined the difference of performance in decodability of instantaneous LDA decoders of trial type using
simultaneous recording and its trial-blind shuffled data, where a minimum number of simultaneous recording units
are > 5 and number of trials are > two times of the recording units (where overfit of coefficients should be in 
principal avoided in analysis).
```{r}
source('Dataset_Comparison_Funcs.R')
Datasets <- c('Simultaneous_Spikes', 'Simultaneous_Ca_Slow_Short_Delay_Virus', 'Simultaneous_Ca_Slow_Short_Delay')
ImageDir <- 'SimultaneousUnitsDecodability/SimultaneousLDA_'
includeVerticalPieMD(ImageDir, Datasets=Datasets, fileType = 'svg')
```



### Supplementary Figure `r figIndex`g -- Decodability of stimulus using spike to calcium model

### Supplementary Figure `r figIndex`h -- Decodability of epoch using spike to calcium model