```{r, echo=FALSE}
figIndex <- 2
```

---
title: `r paste("Supplementary Figure ", figIndex, sep='')`
author: "Ziqiang Wei"
date: '`r Sys.Date()`'
output:
  html_document:
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, results='asis')
```


```{r}
source('Dataset_Comparison_Funcs.R')
ImageDir <- 'SingleUnitsAnova/SingleUnitsAnovaDynamic_'
includeColorbarMD(ImageDir)
```

## Fraction of mixed-selective neurons is distributed similarly at different locations

3-anova analysis (AAV 4.12: ; Transgeneic: 735 neuron)


#### Supplementary Figure `r figIndex`a -- Fraction of mixed-selective neurons is distributes similarly at different depths
```{r}
source('Dataset_Comparison_Funcs.R')
ImageDir <- 'SingleUnitsAnova/SingleUnitsAnovaDepth_'
includeHtmlMD(ImageDir)
```

#### Supplementary Figure `r figIndex`b -- Fraction of mixed-selective neurons is distributes similarly at different AP-ML locations
```{r}
apmlDatasets <- c('Pop_SShuffleConfounding_Ca_Slow_Long_Delay', 'Sub_SShuffleConfounding_Ca_Slow_Long_Delay')
apmlDatasetsName <- c('Whole population', 'Sub-population')
ImageDir <- 'ConfoundingFactorAnova/SingleUnitsAnovaAPML_'
source('Dataset_Comparison_Funcs.R')
includeHtmlMD(ImageDir, Datasets = apmlDatasets, DatasetsName=apmlDatasetsName)
```


#### Supplementary Figure `r figIndex`c -- Fraction of mixed-selective neurons is distributes similarly across different animals
```{r}
anmDatasets = c('ShuffleConfounding_Spikes', 'ShuffleConfounding_Ca_Slow_Short_Delay_Virus')
anmDatasetsName = c('Spike', 'AAV: GP4.12')
ImageDir = 'ConfoundingFactorAnova/SingleUnitsAnovaANM_'
source('Dataset_Comparison_Funcs.R')
includeHtmlMD(ImageDir, Datasets = anmDatasets, DatasetsName=anmDatasetsName)
```